Notes on conformal manifolds

### 2025-06-17 Draft_MLFlatDirections.tex
replace flowchart

		Once the Annealing loop is over, we end up with a total of $n_{sample}$ particles, which in principle should be close to annihilate our data, but whose coefficient may need some more fine tuning. To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a pertubation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller. This allow to fine-tune the coefficients. 
\hspace{-2cm}
\begin{center}
	\begin{minipage}{18cm}
		\begin{tcolorbox}[colback=myblue!5,
			colframe=myblue,
			title=Algorithm flowchart for ASMC algorithm,
			halign title=flush center,
			sharp corners
			]
%	\scalebox{0.5}{
\begin{tikzpicture}[node distance=1.8cm and .5cm]

@@

	\draw [arrow] (exploit) -- (output);
	\draw [arrow] (output) -- (stop);
		\end{tikzpicture}
		\end{tcolorbox}
\end{minipage}
\end{center}
%		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold). Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate. Total time needed, without cluster or fancy computers.}
	%\end{itemize}

  In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field. In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$. That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.

>>>>

		Once the Annealing loop is over, we end up with a total of $n_{sample}$ particles, which in principle should be close to annihilate our data, but whose coefficient may need some more fine tuning. To deal with it, we ran a quick exploitation phase, where, for each polynomial, we now only modify its coefficients, with a pertubation $\epsilon \sim \mathcal{N}(0, \sigma_1)$, and keep the new particle, only if the Loss function is now getting smaller. This allow to fine-tune the coefficients.

%		\bd{Results for naive choices of parameters (numbers of iteration and particles, probabilities, $\beta$) and motivate them (we want some exploration and then exploitation, not too long computations): for multiple runs we find multiple polynomials (good polynomial: after exploitation we convert the coefficients to integers and square roots, and recompute loss without regularisation, select with threshold). Quantify it nicely: success rates for each polynomials, and absolute number of success, failing rate. Total time needed, without cluster or fancy computers.}
	%\end{itemize}

  In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field. In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with
  \begin{center}
  	\begin{minipage}{18cm}
  		\begin{tcolorbox}[colback=myblue!5,
  			colframe=myblue,
  			title=Algorithm flowchart for ASMC algorithm,
  			halign title=flush center,
  			sharp corners
  			]
  			%	\scalebox{0.5}{
  				\begin{tikzpicture}[node distance=1.8cm and .5cm]

@@

  					\draw [arrow] (exploit) -- (output);
  					\draw [arrow] (output) -- (stop);
  				\end{tikzpicture}
  			\end{tcolorbox}
  		\end{minipage}
  	\end{center}
  	coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$. That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
